Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
Started conclusions

\section*{Acknowledgements}
It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
Ross Fadely (NYU), and Alan Heavens (Edinburgh)
for valuable discussion.

This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.

@@

\bibitem[\protect\citeauthoryear{Green}{1995}]{rjmcmc}
Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.

>>>>

\section{Conclusions}
We have developed a trans-dimensional Bayesian approach motivated directly by
the question of whether dark substructures exist in a lens galaxy, given image
data. By making use of the Diffusive Nested Sampling algorithm \citep{dnest}
and the {\tt RJObject} library \citep{rjobject}, we outsource the difficulties
associated with choosing Metropolis proposals for a hierarchical model of
non-fixed dimension. The model allows for source and lens ``blobs'' to appear
as needed to explain the data.

\section*{Acknowledgements}
It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
Ross Fadely (NYU), and Alan Heavens (Edinburgh)
for valuable discussion.
This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.

@@

\bibitem[\protect\citeauthoryear{Green}{1995}]{green}
Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.
